# Maps of GTFS in R

## gtsf Package

[`gtsf`](https://github.com/r-transit/gtsf) is an R package for using GTFS data as [simple features](https://en.wikipedia.org/wiki/Simple_Features). Simple features are basically data frames with geospatial data ready for cartography and spatial analysis. 

### Installation

You can install this package from CRAN with:

`install.packages("gtsf")`

## Import using trread

Import transit lines from the NYC Subway using `trread`.

```{r, message=FALSE, warning=FALSE, results='hide'}
library(trread)
library(gtsf)
library(dplyr)

NYC <- import_gtfs("http://web.mta.info/developers/data/nyct/subway/google_transit.zip")
```

### Get Geometries/Geography

```{r}
NYC <- gtfs_as_sf(NYC)
```

This adds two simple features dataframes to the list of GTFS objects:
-stops_sf 
-routes_sf

### Make Maps

These can be mapped with various libraries. For example, with the [tmap](https://cran.r-project.org/web/packages/tmap/vignettes/tmap-nutshell.html) package:

```{r}
library(tmap)
routes_sf <- NYC$sf_routes
qtm(routes_sf)
```

### Export GTFS

#### GeoJSON 

They can also be exported to GeoJSON or Shapefile, for use in other software. For example:

```{r, eval=FALSE}
library(sf)
st_write(NYC$sf_routes,"nyc_routes.geojson")
```

#### Shapefile

```{r, eval=FALSE}
library(sf)
st_write(NYC$sf_routes,"nyc_routes.shp")
```
